A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-14 manuscript.Rmd
moved t test part to limitations

Please note that the procedure of running different test procedures based on a fixed skewness threshold was created for didactic purposes and it is not necessarily optimal for adressing your research question.
The t-test and Mann–Whitney–Wilcoxon test are arguably the most often used hypothesis test [@fagerlandTtestsNonparametricTests2012; @hortonStatisticalMethodsJournal2005 reports that 26% of all studies employ a t-test and 27% employ a rank based alternative in the New England Journal of Medicine in 2005].
The analytical strategy presented here is in fact suboptimal with regard to several criteria (untested assumption of measurement invariance [@putnickMeasurementInvarianceConventions2016], underestimation of effect size in presence of measurement error [@frostCorrectingRegressionDilution2000], overestimation of effect size for highly skewed distributions [@stonehouseRobustnessTestsCombined1998]). <!--AB can we move this to a different place? Maybe this would actually better fit to the discussion/limitation section!-->

To use this function one needs a compatible dataset. <!--AB what is "this" function? What does "compatible" mean?-->
At the time of preregistration there is of course no actual data available.
We therefore simulate a dataset first that resembles the expected structure of the empirical data that we will use for the final analysis.

@@

Using the `report` package, we can obtain a preview of how our reporting will look like based on simulated data:

@@

<!--AB: add limitations; move the t-test discussion on non-optimality here TODO-->

>>>>

<!--AB here is kind of a break in the text-->
To use this function one needs a compatible dataset. <!--AB what is "this" function? What does "compatible" mean?-->
At the time of preregistration there is of course no actual data available.
We therefore simulate a dataset first that resembles the expected structure of the empirical data that we will use for the final analysis.
Using the simulated dataset as placeholder, we can now write a scientific report including all analysis code blocks and the presentation of results, which can serve as PAC.
The following code simulates a dataset with one observed variable in two groups.

@@

Next, we add dynamic code blocks to our Markdown report that implement the planned reporting of the final results.
A variety of packages automatically generate well formatted outputs of statistical reports or even entire tables of estimates or figures. <!--AB add citations to some of the packages papaja? stargazer? and more...-->
Here we use the `report` package to create a preview of how our reporting will look like based on simulated data:<!--AB add citation to the report package-->

@@

<!--AB: add limitations; move the t-test discussion on non-optimality here TODO-->
Please note that the procedure of running different test procedures based on a fixed skewness threshold was created for didactic purposes and it is not necessarily optimal for adressing your research question.
The t-test and Mann–Whitney–Wilcoxon test are arguably the most often used hypothesis test [@fagerlandTtestsNonparametricTests2012; @hortonStatisticalMethodsJournal2005 reports that 26% of all studies employ a t-test and 27% employ a rank based alternative in the New England Journal of Medicine in 2005].
The analytical strategy presented here is in fact suboptimal with regard to several criteria (untested assumption of measurement invariance [@putnickMeasurementInvarianceConventions2016], underestimation of effect size in presence of measurement error [@frostCorrectingRegressionDilution2000], overestimation of effect size for highly skewed distributions [@stonehouseRobustnessTestsCombined1998]). <!--AB can we move this to a different place? Maybe this would actually better fit to the discussion/limitation section!-->
